New insights into the Weddell Sea ecosystem applying a network approach

### 2022-12-26 Manuscript/Manuscript.Rmd
Review completed

<!-- Objectives -->
In this work we aim to go beyond the trophic knowledge of who eats whom in the Weddell Sea ecosystem by providing a quantitative approach to the already described complex network of feeding interactions. Within this framework we also aim to analyse the species' properties and role in the structure and stability of the food web. To achieve this we: 1) estimated the strength for each interaction in the Weddell Sea food web, 2) characterised species considering weighted and unweighted properties, and 3) analysed the species’ role in the stability of the food web.

@@

<!--LAS up to here -->

@@

The statistical distribution that best fitted the empirical interaction strength distribution of the Weddell Sea food web was a ‘gamma’ due to the high proportion of weak interactions and the existence of a few strong interactions (Figure 3, Table S3).

@@

Our analyses show that the distribution of species interaction strength at the network level is asymmetric, i.e., the Weddell Sea food web contains many weak interactions and only a few strong ones. This finding is consistent with many previous theoretical and empirical studies [e.g. @McCann1998; @Neutel2002; @Emmerson2004; @Wootton2005; @Kortsch2021]. The asymmetric distribution of interaction strength in food webs has been interpreted as an explanation for the persistence of complex communities in nature [@Bascompte2005; @Allesina2015; @Nilsson2016]. Here we show that this pattern is also prevalent in one of the most complex empirical (marine) food webs to date, comprising 490 species and 16041 predator-prey interactions. This finding reinforces the call for the inclusion of interaction strength in food web studies to better understand the ecosystem functioning, and species and whole network responses to environmental perturbations.

@@

We employed a range of descriptors using both unweighted and weighted food web properties to characterise the dynamic and multifaceted nature of the Weddell Sea food web. Our results show a positive relationship between interaction strength and trophic level, and between interaction strength and species degree. Mean interaction strength increases with trophic level and species degree. The former relationship might contradict those studies that suggest that mid-trophic level species are involved in the major pathways of energy flow in high-latitude marine ecosystems [@Pinkerton2014; @Murphy2016; @McCormack2020; @Riccialdelli2020]. This could be explained by the lack of species biomass data in our interaction strength estimations; the methodology we applied here [@Pawar2012] allows empirical data for the density of the resource to be included, though this data is not for the majority of  food web species at the study site. On the other hand, the positive relationship between interaction strength and degree reinforces the importance of species with many interactions: species with high degree (hubs) have a large impact on overall food web structure and functioning [@Dunne2002a; @Kortsch2015]. In the Weddell Sea, species with high degree also tend to have high mean interaction strengths. This information on the quantity and quality of interactions and its relationship enables a robust assessment of the species’ role in the stability of the food web [@Cirtwill2018a].

@@

Only a few species play a key role with respect to the Weddell Sea food web stability, according to the mean maximum eingenvalue stability index employed in this study. This is in concordance with other studies on complex empirical food webs in marine ecosystems in the Arctic and other locations in Antarctica [@Kortsch2015; @Marina2018; @Rodriguez2022]. These key species are characterised by a particular set of food web properties: high to mean interaction strength; mid to high trophic level; relatively high number of interactions; and mid to low trophic similarity. In a previous study on sequential extinction simulations for the Weddell Sea food web, it was found  that larger bodied-sized species could be lost without causing a collapse of the network. A major caveat of this finding, also recognised by the authors, was that population dynamics were ignored and hence no top-down extinctions, or other indirect effects, could occur. In our study we considered such top-down effects by including information on the species interaction strength, which is of paramount importance when analysing the response of perturbations in ecological communities [@McCann1998; @Montoya2009; @Novak2011]. Thus, our study suggests that species with high mean interaction strength and high trophic level need to be considered with particular attention when trying to predict the effects of perturbations on the Weddell Sea ecosystem. This conclusion is further reinforced by the finding that these species have mid to low trophic similarity, which means that few other species of the food web can occupy the same trophic role. In a review, it was emphasised that polar pelagic communities are particularly sensitive to changes due to a low functional redundancy at key trophic levels [@Murphy2016]. Here we provide broader analyses of species impact on food web robustness by including species from all habitats (benthic, pelagic and land-based). This suggests that the sensitivity of marine polar ecosystems to environmental perturbations is a concern also beyond the pelagic realm.

@@

Our study goes beyond the current understanding of how species influence ecosystem structure and stability in the Weddell Sea in particular and in most polar regions in general [@Murphy2016; @McCormack2021]. In the same analysis we have integrated information about weighted (interaction strength) and unweighted species properties, enabling a more complete assessment of the species’ role in the food web structure and function, likely highlighting the ecological processes at play in the Weddell Sea ecosystem.

@@

>>>>

<!-- LAS I think that the methodology of estimating the IS is in the heart of the paper so we need to say something about that, this is why I added the following paragraph-->
Several methodologies have been applied to estimate the interaction strength in food webs, where the quantity and quality of data mostly determine which approach is more convenient [@Berlow2004]. Experimental methods combined with dynamic modelling [@Emmerson2004; @Carrara2015], measurements of species abundances trough time [@Fahimipour2014; @Chang2021], and/or estimation of metabolic rates and biomass of all species in the community [@Neutel2014]; all these methods require a large experimental and/or sampling effort that restrict them to simple networks (circa 10 species). Other methods based on predator-prey body mass allometric relationships [@Berlow2009; @Pawar2012] could be applied to larger networks due to less data requirements, although they might have less power with increasingly complex networks unless more traits are included in the estimations [@Jonsson2018]. For food webs composed by nearly 1000 species and about 20000 interactions only those methods with less data requirements are feasible. On of these is the one proposed by @Pawar2012, which allows to obtain interaction strength estimations by combining data on body mass (of consumer -predator- and resource -prey-) and interaction dimensionality (classified as 2 or 3 dimensions).

<!-- Objectives -->
In this work we aim to go beyond the trophic knowledge of who eats whom in the Weddell Sea ecosystem by providing a quantitative approach to the already described complex network of feeding interactions. Within this framework we also aim to analyse the species' properties and role in the structure and stability of the food web. To achieve this we: 1) estimated the strength for each interaction in the Weddell Sea food web, 2) characterised species considering weighted and unweighted properties, and 3) analysed the species’ role in the stability of the food web. This is the first time that the interaction strength was estimated for all the interactions mostly at the species level for the Weddell sea food web

@@

@@

The statistical distribution that best fitted the empirical interaction strength distribution of the Weddell Sea food web was a ‘gamma’ due to the high proportion of weak interactions and the existence of a few strong interactions (Figure 3, Table S3). <!-- Gamma parameters ?? -->

@@

We estimated for the first time all the interaction strengths (IS) of the Weddell food web. Our analyses show that the distribution of species IS at the network level is asymmetric, i.e., the Weddell Sea food web contains many weak interactions and only a few strong ones. This finding is consistent with many previous theoretical and empirical studies [e.g. @McCann1998; @Neutel2002; @Emmerson2004; @Wootton2005; @Kortsch2021]. The asymmetric distribution of IS in food webs has been interpreted as an explanation for the persistence of complex communities in nature [@Bascompte2005; @Allesina2015; @Nilsson2016]. Here we show that this pattern is also prevalent in one of the most complex empirical (marine) food webs up to date, comprising 490 species and 16041 predator-prey interactions. This finding is in someway validating the method we used, validation of allometric methods of IS estimation not including interaction dimensionality has been performed for microcosmos of relatively few species [@Jonsson2018]. <!--This finding reinforces the call for the inclusion of IS in food web studies to understand better the ecosystem functioning, and species and whole network responses to environmental perturbations.-->

@@

We employed a range of descriptors using both unweighted and weighted food web properties to characterise the dynamic and multifaceted nature of the Weddell Sea food web. Our results show a positive relationship between IS and trophic level and between IS and species degree. Mean IS increases with trophic level and species degree. The former relationship might contradict those studies that suggest that mid-trophic level species are involved in the major pathways of energy flow in high-latitude marine ecosystems [@Pinkerton2014; @Murphy2016; @McCormack2020; @Riccialdelli2020]. This could be explained by the lack of species biomass data in our IS estimations; the methodology we applied here [@Pawar2012] allows empirical data for the density of the resource to be included, though this data is not present for the majority of food web species at the study site. On the other hand, the positive relationship between IS and degree reinforces the importance of species with many interactions: species with high degree (hubs) have a large impact on overall food web structure and functioning [@Dunne2002a; @Kortsch2015]. In the Weddell Sea, species with a high degree also tend to have high mean ISs. This information on the quantity and quality of interactions and their relationship enables a robust assessment of the species’ role in the stability of the food web [@Cirtwill2018a].

@@

Only a few species play a key role with respect to the Weddell Sea food web stability, according to the mean maximum eigenvalue stability index employed in this study. This is in concordance with other studies on complex empirical food webs in marine ecosystems in the Arctic and other locations in Antarctica [@Kortsch2015; @Marina2018; @Rodriguez2022]. These key species are characterised by a particular set of food web properties: high to mean IS; mid to high trophic level; a relatively high number of interactions; and mid to low trophic similarity. In a previous study on sequential extinction simulations for the Weddell Sea food web [@CITA!!!], it was found  that larger bodied-sized species could be lost without causing a collapse of the network. A major caveat of this finding, also recognised by the authors, was that population dynamics were ignored and hence no top-down extinctions, or other indirect effects, could occur. In our study we considered such top-down effects by including information on the species IS, which is of paramount importance when analysing the response of perturbations in ecological communities [@McCann1998; @Montoya2009; @Novak2011]. Thus, our study suggests that species with high mean IS and high trophic levels need to be considered with particular attention when trying to predict the effects of perturbations on the Weddell Sea ecosystem. This conclusion is further reinforced by the finding that these species have mid to low trophic similarity, which means that few other species of the food web can occupy the same trophic role. In a review, it was emphasised that polar pelagic communities are particularly sensitive to changes due to a low functional redundancy at key trophic levels [@Murphy2016]. Here we provide broader analyses of species impact on food web robustness by including species from all habitats (benthic, pelagic and land-based). This suggests that the sensitivity of marine polar ecosystems to environmental perturbations is a concern also beyond the pelagic realm.

@@

Our study goes beyond the current understanding of how species influence ecosystem structure and stability in the Weddell Sea in particular and in most polar regions in general [@Murphy2016; @McCormack2021]. In the same analysis we have integrated information about weighted (IS) and unweighted species properties, enabling a more complete assessment of the species’ role in the food web structure and function, likely highlighting the ecological processes at play in the Weddell Sea ecosystem.

@@

<!-- LAS Figure 2 is confusing, on the left side the title is "Weighted" but the network seems unweighted, I would delete the small predator-prey on the left, and explain that arrow are the flux of energy thus pointin to the predator, and that IS is represented by the width of the arrow. -->

### 2022-12-26 Manuscript/Manuscript.tex
Review completed

\introduction[Introduction]

The objective of this work was to improve the knowledge on how the
Weddell Sea and the species therein may respond to perturbations from
ongoing environmental changes. To achieve this we: 1) estimated the
strength for each interaction in the Weddell Sea food web, 2)
characterised species considering weighted and unweighted properties,
and 3) analysed the species' role in the stability of the food web.

@@

The Weddell Sea food web was retrieved from the GlobAL daTabasE of
traits and food Web Architecture (GATEWAy, version 1.0) of the German
Centre for Integrative Biodiversity Research (iDiv) Halle-Jena-Leipzig
\citep{Brose2018}. In addition to predator-prey interactions, the
database contains information on other biological data such as the mean
body mass and movement type for each species in the food web.
Furthermore, it incorporates information about the interaction itself,
such as the dimension of the predator search space (2 or 3 dimensions).
In its current form the Weddell Sea food web comprises 490 species and
16041 predator-prey interactions and constitutes one of the most
resolved food webs constructed to date \citep{Jacob2011}.

@@

To estimate the strength of each pairwise interaction in the food web we
followed the methodology proposed by \citet{Pawar2012}. The minimum data
requirements are body mass of the consumer (predator) and resource
(prey), and the interaction dimensionality (ID) classified as 2 or 3
dimensions. The ID is defined as the dimension of the search space of
the predator, that is equivalent to the movement space of the prey.
Thus, the ID is classified as 2D when both predator and prey move in 2D
(e.g., both are benthic) or if a predator moves in 3D and a prey in 2D
(e.g., pelagic predator on benthic prey). The ID is classified as 3D
when both predator and prey move in 3D (e.g., both pelagic) or if the
predator moves in 2D and the prey in 3D (e.g., benthic predator, pelagic
prey) \citep{Pawar2012}. GATEWAy v.1.0 provides information on the mean
body mass for consumers and resources, except for `detritus' and
`sediment', and the dimensionality for the majority of the interactions,
though the latter is missing in some cases (924 interactions). To
complete the missing data on species `dimensionality', we used
information about the movement type of predators and prey included in
GATEWAy.

@@

We obtained estimates for resource density and the search rate from the
scaling relationships with the resource and the consumer mass,
respectively \citep{Pawar2012}. The coefficients of such relationships,
determined by ordinary least squares regression, vary with the
interaction dimensionality. On one hand, resource density scales with
resource mass as power-law with exponents in 2D and in 3D. Since mean
mass for resources `phytodetritus' and `sediment' were not available in
GATEWAy, we considered the body mass of the smallest phytoplankton
species (`Fragilariopsis cylindrus') as a proxy. This is justified by
the fact that `phytodetritus' and `sediment' are mainly composed of dead
or senescent phytoplankton reaching the seabed \citep{Wolanski2011}. On
the other hand, search rate scales with consumer mass as power-law with
exponents in 2D and in 3D.

We fitted six candidate models (Exponential, Gamma, log-Normal, Normal,
Power-law and Uniform) the interaction strength distribution using
maximum likelihood \citep{McCallum2008}, and selected the best fitting
model by computing the Akaike Information Criterion AIC
\citep{Burnham2002}.

@@

To assess species roles as a function of the weighted food web, we
focused on mean interaction strength defined as the average strength of
all interactions for a given species. Further we calculated three
unweighted species properties: a) species degree, i.e., the sum of in-
and out-going interactions ; b) trophic level ; and c) trophic
similarity, i.e., the trophic overlap based on shared and unique
resources and consumers. These metrics were chosen to assess a species
role based on the unweighted food web. The species degree has often been
equated with species importance to the structure and functioning within
a food web, i.e.~perturbations to high-degree species may therefore have
more significant effects on the food web robustness to perturbations
than low-degree species
\citetext{\citealp{Dunne2002a}; \citealp[references
in][]{Cirtwill2018a}}. The trophic level offers information about how
important a species is to its biotic community, i.e., top predators and
primary producers are expected to have particularly large effects on the
rest of their communities through top-down and bottom-up control,
respectively \citep[references in][]{Cirtwill2018a}. Trophic similarity
is an index of trophic overlap considering the set of prey and predators
for a pair of species; it measures one of the most important aspects of
species' niches, the trophic niche, and functional aspects of
biodiversity \citep{Martinez1991, Williams2000}.

Furthermore, we took a species' habitat into account, which describes
the physical position of a species within the ecosystem. Species were
categorised as: 1) benthic, if a species lives on the seafloor; 2)
pelagic, if a species lives close to the surface; 3) benthopelagic, if
it moves between and connects the mentioned environments; 4) demersal,
if it lives and feeds on or near the bottom of the sea; and 5)
land-based, if the consumer is not strictly aquatic but feeds
predominantly on marine species. Species habitat affiliation was
retrieved from \citet{Jacob2011}.

With the aim of studying the relationship between the interaction
strength of the species (weighted property) and its unweighted
properties we performed linear regression analyses between the log mean
interaction strength and each of the mentioned unweighted properties.
Thus we considered the interaction strength as the dependent variable
and the given unweighted property as the independent variable, and
obtained the coefficients (slope and intercept) for the linear model.
Models were fitted using the least squares approach. We also explored
the mean interaction strength distribution with the species habitat.

@@

To analyse the impact of species on food web stability, we performed
extinction simulations deleting one species at a time, that is for every
extinction network size was reduced by one species only. After each
extinction, we calculated the stability of the network minus the
targeted species (489 nodes) and compared it with that of the whole
network (490 nodes in total). To calculate stability, we used the mean
of the real part of the maximum eigenvalue of the Jacobian matrix using
randomized Jacobians and keeping the predator-prey sign structure fixed
\citep{Allesina2008, Grilli2016}. This index indicates a more stable
food web when it is negative. We performed 1000 simulations for each
species extinction and obtained a mean maximum eigenvalue for each case.
At last we statistically analysed such a difference with an
Anderson-Darling test considering a p-value \textless{} 0.01
\citep{Scholz1987}. If this difference is positive, then the stability
of the food web is higher if a species was removed, and vice versa. A
detailed description on the stability calculations can be found in
Supplementary Material.

Once we had the results for the impact on stability for each species
extinction, we plotted them considering weighted (interaction strength)
and unweighted properties, and species habitat. With this we aim to
characterise those species with a relatively high effect on the
stability of the food web.

>>>>

\section{Introduction}

A network of feeding interactions is an important framework for
understanding ecological community structure and a valuable tool for
conserving biodiversity and ecosystem functioning through management
\citep{Thompson2012}. Although topological food web analyses considering
presence/absence of predator-prey interactions provide important
insights into the structure and functioning of ecological communities
\citep[e.g.][]{Pascual2006, Kortsch2015, Marina2018, Cordone2020, Rodriguez2022},
more information on the nature of an ecological interaction is needed to
effectively charaterise ecosystem dynamics and stability. In this
regard, quantifying the strength of species interactions and the
species' role within this approach is of paramount importance
\citep{Carrara2015, Allesina2015, Nilsson2016, Cirtwill2018a}.

The Weddell Sea is expected to be one of the last regions of the
Southern Ocean where the consequences of climate change will manifest
due to ice cover and ocean currents \citep{Teschke2021}. In this regard,
the Weddell Sea region might be less affected by sea surface warming
compared with other areas of the Southern Ocean. Until then, this region
may serve as a retreat for those Antarctic species which either directly
depend on sea ice (e.g.~krill, emperor penguin, Weddell seal) or have
developed such strong adaptations to the polar temperatures during the
past millennia that their heat tolerance is low (e.g.~most notothenioid
fishes). If a climate change scenario is considered, the Weddell Sea
continental shelf will be probably a sink area and a refuge for highly
cold-adapted species \citep{Griffiths2017}. However, while the essential
large-scale hydrodynamic relationships are relatively well known for
this region \citep{deSteur2019}, information on current distribution,
abundance and sensitivity to climate change in the Weddell Sea is only
partially available for a few species \citep{Houstin2022}.

In the past decades, network science has become a powerful
interdisciplinary approach applied across various spatial scales in
polar regions \citep{Carscallen2012, Santana2013}. Particularly in the
Southern Ocean, important insights have been gained into mechanisms for
energy flow, the relative importance and traits of individual species
and the influence of environmental variables (e.g., sea-ice) on the
structure of local food webs \citep{Cordone2020, Rossi2019}.

The complexity of the network of feeding interactions in the Weddell Sea
ecosystem, particularly in the high continental shelf, was introduced by
\citet{Jacob2011}. It's important to note that this study is the only
one addressing the complexity, structure and stability of the Weddell
Sea's food web as a specific study object. Few other investigations have
considered this food web though in a meta-analysis context
\citep{Brose2019, Perkins2022, Saravia2022}. The network analysed by
\citet{Jacob2011} consisted of 488 species and 16200 predator-prey
interactions. Studying the relationships between trophic structure, body
size and network structure, the authors suggested that the diversity of
predatory species types is essential to better comprehend the Weddell
Sea ecosystem. In an attempt to tackle food web stability they performed
extinction simulations and showed that the removal of small to
medium-sized, and not large, organisms caused a cascade of secondary
extinctions. Overall, this suggests the relative importance of
predators, rather than prey, in the architecture, functioning and
stability of the Weddell Sea food web, which coincides with recent
meta-analyses in natural complex food webs
\citep{Brose2019, Perkins2022}.

In this work we aim to go beyond the trophic knowledge of who eats whom
in the Weddell Sea ecosystem by providing a quantitative approach to the
already described complex network of feeding interactions. Within this
framework we also aim to analyse the species' properties and role in the
structure and stability of the food web. To achieve this we: 1)
estimated the strength for each interaction in the Weddell Sea food web,
2) characterised species considering weighted and unweighted properties,
and 3) analysed the species' role in the stability of the food web.

@@

The Weddell Sea food web was retrieved from the GlobAL daTabasE of
traits and food Web Architecture (GATEWAy, version 1.0) of the German
Centre for Integrative Biodiversity Research (iDiv) Halle-Jena-Leipzig
\citep{Brose2018}. In addition to predator-prey interactions, the
database contains information on other biological data such as the mean
body mass and movement type for each species in the food web.
Furthermore, it incorporates information about the interaction itself,
such as the dimension of the predator search space (2 or 3 dimensions).
In its current form, the Weddell Sea food web comprises 490 species and
16041 predator-prey interactions and constitutes one of the most
resolved food webs constructed to date \citep{Jacob2011}.

@@

To estimate the strength of each pairwise interaction in the food web we
followed the methodology proposed by \citet{Pawar2012}. The minimum data
requirements are the body mass of the consumer (predator) and resource
(prey), and the interaction dimensionality (ID) classified as 2 or 3
dimensions. The ID is defined as the dimension of the search space of
the predator, that is equivalent to the movement space of the prey.
Thus, the ID is classified as 2D when both predator and prey move in 2D
(e.g., both are benthic) or if a predator moves in 3D and prey in 2D
(e.g., a pelagic predator on benthic prey). The ID is classified as 3D
when both predator and prey move in 3D (e.g., both pelagic) or if the
predator moves in 2D and the prey in 3D (e.g., benthic predator, pelagic
prey) \citep{Pawar2012}. GATEWAy v.1.0 provides information on the mean
body mass for consumers and resources, except for `detritus' and
`sediment', and the dimensionality for the majority of the interactions,
though the latter is missing in some cases (924 interactions). To
complete the missing data on species `dimensionality', we used
information about the movement type of predators and prey included in
GATEWAy.

@@

We obtained estimates for resource density and the search rate from the
scaling relationships with the resource and the consumer mass,
respectively \citep{Pawar2012}. The coefficients of such relationships,
determined by ordinary least squares regression, vary with the
interaction dimensionality. On the one hand, resource density scales
with resource mass as a power-law with different exponents in 2D and 3D.
Since mean mass for resources `phytodetritus' and `sediment' were
unavailable in GATEWAy, we considered the body mass of the smallest
phytoplankton species (`Fragilariopsis cylindrus') as a proxy. This is
justified by the fact that `phytodetritus' and `sediment' are mainly
composed of dead or senescent phytoplankton reaching the seabed
\citep{Wolanski2011}. On the other hand, the search rate scales with
consumer mass as power-law with exponents in 2D and 3D.

After the estimation, we fitted six candidate models for the interaction
strength distribution: Exponential, Gamma, log-Normal, Normal, Power-law
and Uniform. We used maximum likelihood \citep{McCallum2008} for the
fitting, and selected the best model by computing the Akaike Information
Criterion AIC \citep{Burnham2002}.

@@

We calculated three unweighted species properties: a) species degree,
i.e., the sum of in- and out-going interactions; b) trophic level; and
c) trophic similarity, i.e., the trophic overlap based on shared and
unique resources and consumers. These metrics were chosen to assess a
species' role based on the unweighted food web. The species degree has
often been equated with species' importance to the structure and
functioning within a food web, i.e.~perturbations to high-degree species
may therefore have more significant effects on the food web robustness
to perturbations than low-degree species
\citetext{\citealp{Dunne2002a}; \citealp[references
in][]{Cirtwill2018a}}. The trophic level offers information about how
important a species is to its biotic community, i.e., top predators and
primary producers are expected to have particularly large effects on the
rest of their communities through top-down and bottom-up control,
respectively \citep[references in][]{Cirtwill2018a}. The trophic
similarity is an index of trophic overlap considering the set of prey
and predators for a pair of species; it measures one of the most
important aspects of species' niches, the trophic niche, and functional
aspects of biodiversity \citep{Martinez1991, Williams2000}.

Furthermore, we took a species' habitat into account, which describes
the physical position of a species within the ecosystem. Species were
categorised as 1) benthic, if a species lives on the seafloor; 2)
pelagic if a species lives close to the surface; 3) benthopelagic if it
moves between and connects the mentioned environments; 4) demersal if it
lives and feeds on or near the bottom of the sea; and 5) land-based if
the consumer is not strictly aquatic but feeds predominantly on marine
species. Species habitat affiliation was retrieved from
\citet{Jacob2011}.

To assess species' roles as a function of the weighted food web, we
focused on mean interaction strength defined as the average strength of
all interactions for a given species. To study the relationship between
the interaction strength of the species (weighted property) and its
unweighted properties we performed linear regression analyses between
the log mean interaction strength and each of the mentioned unweighted
properties. Thus we considered the interaction strength as the dependent
variable and the given unweighted property as the independent variable
and obtained the coefficients (slope and intercept) for the linear
model. Models were fitted using the least squares approach. We also
explored the mean interaction strength distribution with the species'
habitat.

@@

To analyse the impact of species on the food web stability, we performed
extinction simulations deleting one species at a time, that is for every
extinction network size was reduced by one species only. After each
extinction, we calculated the stability of the network minus the
targeted species (489 nodes) and compared it with that of the whole
network (490 nodes in total). To calculate the stability, we used the
mean of the real part of the maximum eigenvalue of the Jacobian matrix
using randomized Jacobians and keeping the predator-prey sign structure
fixed \citep{Allesina2008, Grilli2016}. This index indicates a more
stable food web when it is negative. We performed 1000 simulations for
each species extinction and obtained a mean maximum eigenvalue for each
case. At last, we statistically analysed such a difference with an
Anderson-Darling test considering a p-value \textless{} 0.01
\citep{Scholz1987}. If this difference is positive, then the stability
of the food web is higher if a species was removed, and vice versa. A
detailed description of the stability calculations can be found in
Supplementary Material.

Once we had the results for the impact on stability for each species
extinction, we plotted them considering weighted (interaction strength)
and unweighted properties, and species habitat. With this, we aim to
characterise those species with a relatively high effect on the
stability of the food web.
